Board games group recomendation using metadata

### 2024-12-09 paper v2/paper v2.tex
fix: no \newline !!!

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{hyperref}
% the following package enables the use of multiline comments:
\usepackage{comment}

@@

\newline
One aspect of the recommendations that is worth mentioning is that the LightFM model is capable of superior results with more diversity. This means that all groups will get recommended different games, but they are tailored to the preferences of each user on a group. This in hand increases the novelty and the serendipity of the recommendations, creating more unique experiences for the users.

\newline
For each different group formation, the results are the same. This is to be expected, since the group formation is based on the preferences of the users, and the recommendations are made based on the preferences of the group. Not on the preferences of the individual users. This is a good sign, beacuase it shows that the model does not overfit to any group formation and it is able to make recommendations based on the preferences of the group.

\newline

>>>>

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{hyperref}
% the following package enables the use of multiline comments:
\usepackage{comment}
\usepackage{amsmath}

@@

One aspect of the recommendations that is worth mentioning is that the LightFM model is capable of superior results with more diversity. This means that all groups will get recommended different games, but they are tailored to the preferences of each user on a group. This in hand increases the novelty and the serendipity of the recommendations, creating more unique experiences for the users.

For each different group formation, the results are the same. This is to be expected, since the group formation is based on the preferences of the users, and the recommendations are made based on the preferences of the group. Not on the preferences of the individual users. This is a good sign, beacuase it shows that the model does not overfit to any group formation and it is able to make recommendations based on the preferences of the group.
